---
title: "Inhibit Switch Tolerance Stack"
author: "Joe Shields"
date: "2017-12-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

So, I took some measurements with calipers, just listening for when the switch clicked (shown below.)

```{r switchMeasurements}
meas <- read.csv('../COTS/ZFswitches/switchStats.csv')

sdMargin <- 8
peapodSlop <- 1.1
flight.free <- mean(meas$t) + sdMargin*sd(meas$t) 
flight.flushSlop <- mean(meas$t) - sdMargin*sd(meas$t)
flight.flush <- flight.flushSlop-1.1
 
flight.free <-  round(flight.free, 1)
flight.flushSlop <-  round(flight.flushSlop, 1)
flight.flush <- round(flight.flush, 1)
```

```{r plot, echo=FALSE}
par.old <- par(mar=c(4,4,3,0))
layout(matrix(1:2, nrow=1), widths=c(3,1))
posRange <- range(c(meas$t, meas$f, meas$b)) 
plot(meas$label, meas$free.position.mm, pch=1, ylim= posRange, 
     ylab='distance from base of switch (mm)', 
     xlab='switch label'
     )
points(meas$label, meas$trigger.position.mm, pch=2)
points(meas$label, meas$bottom.position.mm, pch=3)
abline(h=c(flight.free, flight.flushSlop, flight.flush), lty=c(3,2,1))
plot.new()
par(mar=c(0,0,0,0))
legend('topright', 
       legend=c('free', 'trigger', 'bottom', 'design free', 'peapod slop', 'design flush'), 
       pch=c(1,2,3, NA, NA, NA),
       lty=c(NA,NA,NA, 3,2,1)
       )
par(par.old)
```

It seems like the spread between the relevant positions is large enough compared to the standard deviation that we don't really need to worry about the statistics of switch production. I set this to give us a comfy $8\sigma$ margin around the switch trigger.

- Set the geometry such that the end of the arm is `r flight.free` mm away from the base of the switch when free of the peapod.  
- Set the geometry such that the end of the arm is `r flight.flushSlop` mm away from the base of the switch when inside the peapod and pushed away from the wall.  
- Set the geometry such that the end of the arm is `r flight.flush` mm away from the base of the switch when inside the peapod and pushed against the wall.  

If you need to shrink that interval, try to keep it centered around `r round(mean(meas$t), 2)`.


[inhibitReqs]: https://docs.google.com/document/d/1oqqp9OsMruQzNAHI35QE_UZxmF_v83l-TLrQsE882ks/edit?usp=sharing